---
title: "markdownTest"
output: github_document
---

# Script for manuscript organization  

This example was developed for a carpentries workshop  

1. Prepare an R environment  

2. Download and save USGS data

3. Tidy data  

4. Report  

## 1. prepare the R environment  

load libraries 

```{r setup}
knitr::opts_chunk$set(echo=T)
library(dataRetrieval)
library(dplyr)
library(zoo)
library(lubridate)
library(ggplot2)
```


## 2. download data  
use `readNWISdv` function from the dataRetrieval package  to download KS river data
```{r download data}
usgs_id <- "07141220"

data_raw <- readNWISdv(siteNumbers = usgs_id,
                       parameterCd = "00065",
                       startDate = "2018-10-01",
                       endDate = "2021-09-30")
#inspect data  
summary(data_raw)
# save the data
write.csv(data_raw, "data/exampleStreamGaugeData.csv")
```

## Tidy data  

in this section we will perform some basic 

```{r clean data}
# create data frame with better colnames
data_tidy <- data_raw %>% 
  rename(stage_ft = X_00065_00003,
         stage_QAcode = X_00065_00003_cd) %>% 
  select(-agency_cd, -site_no)

# look at dataframe  
head(data_tidy)

# first step is to plot data

ggplot(data=data_tidy, aes(x=Date, y=stage_ft))+
  geom_line()

# deal with missing data by compare to possible days
first_date <- min(data_tidy$Date)
last_date <- max(data_tidy$Date)

all_dates <- seq(first_date, last_date, by = "day")
length(all_dates) == length(data_tidy)

missing_dates <- all_dates[!(all_dates %in% data_tidy$Date)]

# add missing dates

new_dates <- data.frame(Date = missing_dates, state_ft = NA, stage_QAcode = "Gapfill")
data_clean <- bind_rows(data_tidy, new_dates) %>% 
  arrange(Date)

summary(data_clean)

# fill in those gaps 

data_clean$stage_ft <- na.approx(data_clean$stage_ft)

summary(data_clean)

# need to fix gapfill and pass QA code
```


## 4. Write up some summary stats  

We analyzed `r usgs_id`.  The max stage was `r max(data_clean$stage_ft)` feet.

